Social Visual Analytics: DevOps for Data Scientists

### 2015-03-25 relatedwork.tex
intro and related work

>>>>

There is much previous work that inspired or influenced ours.
Indeed, many studies have addressed the requirements for future visual
analytics environments.
Previous work that we learned from includes:

{\bf Vistrails} as a landmark prototype of a scientific workflow
and provenance management system. This prototype helped the community
to understand the value of capturing aspects of the processes that
surround data analysis experiments and tools, including detailed
history, collaboration, and deployment.

{\bf iPython notebooks (Jupyter)} are the closest work we are aware of.
The goal of this project is to provide shared notebooks and a remote
execution environment for interpreted scripts. \stephen{Are there 
significant differences involving versioning, provenance, annotation
and other broad process support?}

{\bf RStudio, RShiny} and other packages based on R for creating and
publishing web content such as knitR, Rpubs, rCharts, and gg2v.
These tools are not collaborative, but they are aimed at better
graphics and web applications.

{\bf bl.ocks, jsfiddle, plotly} and other web services for sharing code
and demos.

{ManyEyes} is the best-known original work showing the potential for
integrating data visualization with social media.

Further afield, {\bf Electronic Lab Notebooks} are applications for organizing
and sharing data from scientific lab experiments\cite{Rubacha:2011:ELN}.
In a sense, we hope to adapt and extend this concept to the work of
visual analytics teams.
